Constrained, yet diverse: Phylogenetic and morphological filtering in epiphytic ferns

### 2019-08-15 ms/SI.rmd
Move SI files to ms/ folder

---
title: ""
output: word_document
---

@@

```{r}
trait_data_for_si %>%
  write_csv(here::here("si/Table_S2.csv"))
```

@@

```{r climate-ancova}
# Format and write out table as CSV file
climate_ancova_results %>% 
  mutate(
    p.value = signif(p.value, 2) %>% format.pval(., digits = 1),
    meansq = round_t(meansq, 2),
    term = case_when(
      term == "habit" ~ "Growth habit",
      term == "el" ~ "Elevation",
      term == "habit:el" ~ "Growth habit × elevation",
      TRUE ~ term
    )
  ) %>%
  select(`Response variable` = variable, `Source of variation` = term, `d.f.` = df, MS = meansq, P = p.value) %>%
  write_csv(here::here("si/Table_S3.csv"))

@@

```{r phylosig-binary-strict}
# Format and write out table as CSV file
phylosig_binary_traits_strict %>%
  mutate(D = round_t(D, 2)) %>%
  mutate(trait = factor(
    trait, 
    levels = c("habit", "gemmae", "glands", "hairs","morphotype"))) %>%
  mutate(trait = lvls_revalue(
    trait,
    new_levels = c("Epiphytic growth", "Gemmae", "Glands", "Hairs", "Cordate morphotype"))) %>%
  arrange(trait) %>%
  select(Trait = trait, `Number of presences` = num_present, `Number of absences` = num_absent, D,
         P_rnd = prob_random, P_bm = prob_brownian) %>%
  write_csv(here::here("si/Table_S4.csv"))
```

@@

```{r corr-evo-strict}
# Format and write out table as CSV file
correlated_evo_test_strict %>%
  mutate(trait = factor(
    trait, 
    levels = c("gemmae", "glands", "hairs","morphotype"))) %>%
  mutate(trait = lvls_revalue(
    trait,
    new_levels = c("Gemmae", "Glands", "Hairs", "Morphotype"))) %>%
  arrange(trait) %>%
  select(
    Trait = trait,
    `LL (independent model)` = logL_indep,
    `LL (dependent model)` = logL_dep,
    `Likelihood ratio` = likelihood_ratio,
    `P` = pval
  ) %>%
  write_csv(here::here("si/Table_S5.csv"))
```

@@

```{r best-fit-mods}
# Format and write out table as CSV file
best_fit_div_models_moran %>%
  # Drop frond length and width (highly correlated with rhizome dia.)
  filter(resp_var %in% c("ntaxa", "mpd.obs.z.phy", "mntd.obs.z.phy", 
                   "mpd.obs.z.func", "mntd.obs.z.func",
                   "dissection", "sla", "stipe", "rhizome", "pinna")) %>%
  mutate(resp_var = factor(
        resp_var, 
        levels = c("ntaxa", "mpd.obs.z.phy", "mntd.obs.z.phy", 
                   "mpd.obs.z.func", "mntd.obs.z.func",
                   "dissection", "sla", "stipe", "rhizome", "pinna"))) %>%
  mutate(
    resp_var = lvls_revalue(
        resp_var, 
        new_levels = c("Richness", "MPDphy", "MNTDphy", 
                       "MPDfunc", "MNTDfunc",
                       "Dissection", "SLA", "Stipe length", "Rhizome diam.", "Pinna no.")) 
  ) %>%
  arrange(resp_var, delta_AICc) %>%
  mutate(
    modname = modname %>%
      str_replace_all("\\+", " \\+ ") %>%
      str_replace_all("\\.by\\.", " x ") %>%
      str_replace_all("habit", "Growth habit") %>%
      str_replace_all("temp_mean", "Mean temp.") %>%
      str_replace_all("temp_sd", "SD temp.") %>%
      str_replace_all("temp_max", "Max. temp.") %>%
      str_replace_all("vpd_mean", "Mean VPD") %>%
      str_replace_all("vpd_sd", "SD VPD") %>%
      str_replace_all("vpd_min", "Min. VPD")
  ) %>% 
  select(
    `Metric` = resp_var,
    `Model` = modname,
    AICc,
    `R2` = r2,
    delta_AICc,
    `Moran's I` = morans_I,
    `P_moran` = morans_I_pval
  ) %>%
  write_csv(here::here("si/Table_S6.csv"))
```

@@

ggsave(plot = fig_s1, filename = here("si/Fig_S1.pdf"), height = 8, width = 4, units = "in")
```

>>>>

---
title: ""
bibliography: "si_references.bib"
mainfont: Times New Roman.ttf
fontsize: 12pt
mainfontoptions: 
- BoldFont=Times New Roman Bold.ttf
- ItalicFont=Times New Roman Italic.ttf
- BoldItalicFont=Times New Roman Bold Italic.ttf
output: 
  bookdown::pdf_document2:
    citation_package: none # Use pandoc default, otherwise csl can't be used for reference formatting
    toc: no
    number_sections: no
    fig_caption: yes
    keep_tex: no
    latex_engine: xelatex
    pandoc_args: [ "--csl", "new-phytologist.csl"]
nocite: | 
  @NMNS2008, @Copeland1932, @FloraNSW2019, @Brownsey1987, @Murdock2003
---

@@

```{r}
trait_data_for_si %>%
  write_csv(here::here("ms/Table_S2.csv"))
```

@@

```{r climate-ancova}
# Format and write out table as CSV file
climate_ancova_results %>% 
  mutate(
    p.value = signif(p.value, 2) %>% format.pval(., digits = 1),
    meansq = round_t(meansq, 2),
    term = case_when(
      term == "habit" ~ "Growth habit",
      term == "el" ~ "Elevation",
      term == "habit:el" ~ "Growth habit × elevation",
      TRUE ~ term
    )
  ) %>%
  select(`Response variable` = variable, `Source of variation` = term, `d.f.` = df, MS = meansq, P = p.value) %>%
  write_csv(here::here("ms/Table_S3.csv"))

@@

```{r phylosig-binary-strict}
# Format and write out table as CSV file
phylosig_binary_traits_strict %>%
  mutate(D = round_t(D, 2)) %>%
  mutate(trait = factor(
    trait, 
    levels = c("habit", "gemmae", "glands", "hairs","morphotype"))) %>%
  mutate(trait = lvls_revalue(
    trait,
    new_levels = c("Epiphytic growth", "Gemmae", "Glands", "Hairs", "Cordate morphotype"))) %>%
  arrange(trait) %>%
  select(Trait = trait, `Number of presences` = num_present, `Number of absences` = num_absent, D,
         P_rnd = prob_random, P_bm = prob_brownian) %>%
  write_csv(here::here("ms/Table_S4.csv"))
```

@@

```{r corr-evo-strict}
# Format and write out table as CSV file
correlated_evo_test_strict %>%
  mutate(trait = factor(
    trait, 
    levels = c("gemmae", "glands", "hairs","morphotype"))) %>%
  mutate(trait = lvls_revalue(
    trait,
    new_levels = c("Gemmae", "Glands", "Hairs", "Morphotype"))) %>%
  arrange(trait) %>%
  select(
    Trait = trait,
    `LL (independent model)` = logL_indep,
    `LL (dependent model)` = logL_dep,
    `Likelihood ratio` = likelihood_ratio,
    `P` = pval
  ) %>%
  write_csv(here::here("ms/Table_S5.csv"))
```

@@

```{r best-fit-mods}
# Format and write out table as CSV file
best_fit_div_models_moran %>%
  # Drop frond length and width (highly correlated with rhizome dia.)
  filter(resp_var %in% c("ntaxa", "mpd.obs.z.phy", "mntd.obs.z.phy", 
                   "mpd.obs.z.func", "mntd.obs.z.func",
                   "dissection", "sla", "stipe", "rhizome", "pinna")) %>%
  mutate(resp_var = factor(
        resp_var, 
        levels = c("ntaxa", "mpd.obs.z.phy", "mntd.obs.z.phy", 
                   "mpd.obs.z.func", "mntd.obs.z.func",
                   "dissection", "sla", "stipe", "rhizome", "pinna"))) %>%
  mutate(
    resp_var = lvls_revalue(
        resp_var, 
        new_levels = c("Richness", "MPDphy", "MNTDphy", 
                       "MPDfunc", "MNTDfunc",
                       "Dissection", "SLA", "Stipe length", "Rhizome diam.", "Pinna no.")) 
  ) %>%
  arrange(resp_var, delta_AICc) %>%
  mutate(
    modname = modname %>%
      str_replace_all("\\+", " \\+ ") %>%
      str_replace_all("\\.by\\.", " x ") %>%
      str_replace_all("habit", "Growth habit") %>%
      str_replace_all("temp_mean", "Mean temp.") %>%
      str_replace_all("temp_sd", "SD temp.") %>%
      str_replace_all("temp_max", "Max. temp.") %>%
      str_replace_all("vpd_mean", "Mean VPD") %>%
      str_replace_all("vpd_sd", "SD VPD") %>%
      str_replace_all("vpd_min", "Min. VPD")
  ) %>% 
  select(
    `Metric` = resp_var,
    `Model` = modname,
    AICc,
    `R2` = r2,
    delta_AICc,
    `Moran's I` = morans_I,
    `P_moran` = morans_I_pval
  ) %>%
  write_csv(here::here("ms/Table_S6.csv"))
```

@@

ggsave(plot = fig_s1, filename = here::here("ms/Fig_S1.pdf"), height = 8, width = 4, units = "in")
```

References
